$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-07-17 paper/paper.tex
Restructure parts of the type system section

%\begin{note}
  \label{note:linearity}
  We will often work with pairs of input and output multiplicities.
  We use the notation $\type{C}^{\func{2}}$ to stand for a $\type{C} \constr{\times} \type{C}$ tuple of input and output multiplicities, respectively.
  We use $\opsquared{x}{y}{z}$ to stand for a monoidal operation on pairs of multiplicities -- where the algebraic laws are lifted element-wise.
%
  Henceforth, we use $\lz$ to denote the pair $0 \comma 0$ for a channel which cannot be used any further, $\li$ for the pair $1 \comma 0$ for a channel to be used in input exactly once, $\lo$ for $0 \comma 1$ for a channel to be used in output exactly once, and $\lio$ for $1 \comma 1$, for a channel to be used exactly once in input and exactly once in output.
  This notation was originally used in the linear \picalc{} \cite{KPT96,Sangio01}.
%\end{note}

@@

\begin{nidefinition}[\textsc{Ctx}: usage contexts]
  A \emph{usage context} is a context $\Ctx_{idxs}$ of usage annotations that is indexed by a length-indexed context of indices $\Idxs_n$ (\autoref{fig:ctx}).

@@

@@

% \begin{note}
  We lift the monoidal operation on usage annotations $\opsquared{x}{y}{z}$ to a monoidal operation $\opctx{\Gamma}{\Delta}{\Xi}$ on usage contexts that have a common underlying context of indices.
  All the properties of the partial monoid are lifted element-wise.
% \end{note}

@@

  The \textsc{VarRef} typing relation for variable references is presented in \autoref{fig:variable-references}.
  \begin{figure}[h]
  \begin{mathpar}
    \mprset{sep=0.5em}

@@

>>>>

@@

\begin{nidefinition}[\textsc{Ctx}: usage contexts]
  A \emph{usage context} is a context $\Ctx_{idxs}$ of pairs of usage annotations that is indexed by a length-indexed context of indices $\Idxs_n$ (\autoref{fig:ctx}).

@@

  We use the notation $\type{C}^{\func{2}}$ to stand for a $\type{C} \constr{\times} \type{C}$ tuple of input and output multiplicities, respectively.
  Henceforth, we use $\lz$ to denote the pair $0 \comma 0$ for a channel which cannot be used any further, $\li$ for the pair $1 \comma 0$ for a channel to be used in input exactly once, $\lo$ for $0 \comma 1$ for a channel to be used in output exactly once, and $\lio$ for $1 \comma 1$, for a channel to be used exactly once in input and exactly once in output.
  This notation was originally used in the linear \picalc{} \cite{KPT96,Sangio01}.

@@

@@

  The \textsc{VarRef} typing relation for variable references is presented in \autoref{fig:variable-references}.

  \begin{figure}[h]
  \begin{mathpar}
    \mprset{sep=0.5em}

@@

  We lift the operation $\op{x}{y}{z}$ and its algebraic properties to an operation $\opsquared{x_l \comma x_r}{y_l \comma y_r}{z_l \comma z_r}$ on pairs of multiplicities and an operation $\opctx{\Gamma}{\Delta}{\Xi}$ on usage contexts with the same underlying context of indices.
